Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-05 paper/snakemajoranas.tex

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
\comment{Hybrid NS structures become topological and are useful for TQC.}
A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,beenakker2016road,leijnse2012introduction}
The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
\comment{Hybrid NS structures become topological and are useful for TQC.}
A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
